---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mutationtypes

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/mutationtypes)](https://CRAN.R-project.org/package=mutationtypes)
<!-- badges: end -->

Say you want to describe the impact of a mutation. There exists several dictionaries you could use, including

1) [Sequence Ontology](http://www.sequenceontology.org/). These terms are what VEP uses

2) [MAF Variant Classification](https://docs.gdc.cancer.gov/Encyclopedia/pages/Mutation_Annotation_Format_TCGAv2/)


**mutationtypes** makes it easy to check whether your vector of mutation types aligns to one of these dictionaries. 
It also simplifies translation from one dictionary to another.


## Installation

You can install the development version of mutationtypes like so:

``` r
# install.packages('remotes')
remotes::install_github('selkamand/mutation_types.R')
```

## Usage

```{r example}
library(mutationtypes)

# Check which mutation impact dictionary you're vector is closest too
mutation_types_identify(
  c(
    "INTRAGENIC", 
    "INTRAGENIC", 
    "intergenic_region", 
    "stop_lost", 
    "missense_variant", 
    "missense_variant"
  )
)

# Convert sequence ontology mutation classes to MAF terms
mutation_types_convert_so_to_maf(
  so_mutation_types = c(
    "INTRAGENIC", 
    "INTRAGENIC", 
    "intergenic_region", 
    "stop_lost", 
    "missense_variant", 
    "missense_variant"
  )
)

# Check what 
```
